Tracing the Stellar Halo of Massive Galaxies to 100 kpc at $0.3<z<0.5$ using the Hyper Suprime-Cam

### 2017-05-25 draft/paper1_jenny.tex
Fig 7: Caption

%% ------------------------------------------------------------------------------------ %% 
  \begin{figure*}
      \centering 
      \includegraphics[width=\textwidth]{fig/redbcg_insitu_accretion}
      \caption{
          \song{New figures to illustrate the assumption of in-situ and accreted mass;
                Need to update the caption.}
          Comparison of the median \mden{} profiles of massive galaxies in the 
          two lower \mtot{} bins from Fig~\ref{fig:avg_prof} with other observations 
          and simulations, focusing on the inner region. 
          The format is similar with the right panel of Fig~\ref{fig:avg_prof}.
          We include: 
          1) the median \mden{} profile of inner component from structure 
          decomposition of massive elliptical galaxies at $z{\sim} 0$ from 
          \citet[][Cyan, solid]{Huang2013a}; 
          2) the median \mden{} profile of massive galaxies at $1.0 < z < 1.5$ 
          from \textit{HST} observations in \citet[][Red, dashed]{Patel2013}; 
          3) the median \mden{} profile of the ``in-situ'' stellar components in 
          simulated massive halos from \citet[][Purple, dot-dashed]{Cooper2013};
          4) the \mden{} profile of the very massive cD galaxy at $z{\sim} 1.1$ 
          discovered by \citet[][Yellow, dashed]{Liu2013} in the Hubble 
          Ultra-Deep Field.}
      \label{fig:discussion_1}
  \end{figure*}
%% ------------------------------------------------------------------------------------ %%

@@

%% ------------------------------------------------------------------------------------ %% 
  \begin{figure*}
      \centering 
      \includegraphics[width=\textwidth]{fig/redbcg_mass_smf}
      \caption{
          \song{New figures to show the impact of mass definition on SMF. 
                Need to update the caption.}
          \textbf{Left}: Relation between \mtot{} and the logarithmic mass difference 
          between \mmax{} and \mtot{} for both \rbcg{} (red square) and \nbcg{} 
          (grey dot) galaxies.  The format is very similar to the left figure of 
          Fig~\ref{fig:mass_complete}.~~
          \textbf{Right}: The stellar mass volume-density distributions of massive 
          galaxies after combining the \rbcg{} and \nbcg{} samples together, using 
          both \mtot{} (black solid line) and \mmax{} (black dash line). 
          The uncertainty for distribution using \mtot{} is shown in grey shaded region.  
          Here, we also compare the distributions with SMF from previous works: 
          (a): SDSS galaxies at $z{\sim} 0.1$ from \citet{Bernardi2013}; the \mstar{} 
          is based on photometry from 2-D \ser{}$+$Exponential model fitting; 
          (b): SDSS galaxies at $z{\sim} 0.1$ from \citet{Moustakas13} based on 
          improved SDSS \texttt{cModel} photometry; 
          (c): \texttt{S82-MGC} galaxies at $0.15 < z< 0.43$ from 
          \citet{Leauthaud2016} based on PSF-matched SDSS-UKIDSS photometry.
          Please see text for more details of the comparison.
          }
      \label{fig:discussion_2}
  \end{figure*}
%% ------------------------------------------------------------------------------------ %%

>>>>

%% ------------------------------------------------------------------------------------ %% 
  \begin{figure*}
      \centering 
      \includegraphics[width=\textwidth]{fig/redbcg_insitu_accretion}
      \caption{
          \textbf{Left:}
          Comparison of the median \mden{} profiles of massive galaxies in the 
          two lower \mtot{} bins from Fig~\ref{fig:avg_prof} with other observations 
          and simulations, focusing on the inner region. 
          The format is similar with the right panel of Fig~\ref{fig:avg_prof}.
          We include: 
          1) the median \mden{} profile of inner component from structure 
          decomposition of massive elliptical galaxies at $z{\sim} 0$ from 
          \citet[][Cyan, solid]{Huang2013a}; 
          2) the median \mden{} profile of massive galaxies at $1.0 < z < 1.5$ 
          from \textit{HST} observations in \citet[][Red, dashed]{Patel2013}; 
          3) the median \mden{} profile of the ``in-situ'' stellar components in 
          simulated massive halos from \citet[][Purple, dot-dashed]{Cooper2013};
          4) the \mden{} profile of the very massive cD galaxy at $z{\sim} 1.1$ 
          discovered by \citet[][Yellow, dashed]{Liu2013} in the Hubble 
          Ultra-Deep Field.
          \textbf{Right:}
          Relation between \mtot{} and the fraction of \mstar{} within 10 to 100 kpc, 
          which is used here as proxy of the fraction of accreted stars. 
          The typical uncertainties of \mtot{} and the mass fraction are shown in 
          upper-left corner. 
          This relation is compared with the relation between \mstar{} and the fraction
          of accreted stars derived from the Illustris simulation at $z=0$ 
          (Fig 4 in \citealt{RodriguezGomez2016}; grey solid and dashed lines). 
          }
      \label{fig:discussion_1}
  \end{figure*}
%% ------------------------------------------------------------------------------------ %%

@@

%% ------------------------------------------------------------------------------------ %% 
  \begin{figure*}
      \centering 
      \includegraphics[width=\textwidth]{fig/redbcg_mass_smf}
      \caption{
          \textbf{Left}: The stellar mass volume-density distributions of massive 
          galaxies after combining the \rbcg{} and \nbcg{} samples together, using 
          both \mtot{} (black solid line) and \mmax{} (black dash line). 
          The uncertainty for distribution using \mtot{} is shown in grey shaded region.  
          Here, we also compare the distributions with SMF from previous works: 
          (a): SDSS galaxies at $z{\sim} 0.1$ from \citet{Bernardi2013}; the \mstar{} 
          is based on photometry from 2-D \ser{}$+$Exponential model fitting; 
          (b): SDSS galaxies at $z{\sim} 0.1$ from \citet{Moustakas13} based on 
          improved SDSS \texttt{cModel} photometry; 
          (c): \texttt{S82-MGC} galaxies at $0.15 < z< 0.43$ from 
          \citet{Leauthaud2016} based on PSF-matched SDSS-UKIDSS photometry.
          Please see text for more details of the comparison.
          }
      \label{fig:discussion_2}
  \end{figure*}
%% ------------------------------------------------------------------------------------ %%
